---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# admtp

<!-- badges: start -->
<!-- badges: end -->

__admtp__ compiles all of the [R](https://www.r-project.org/) code required in the 'Adaptive Designs and Multiple Testing Procedures' course run by [Michael Grayling](https://www.ncl.ac.uk/medical-sciences/people/profile/michaelgrayling.html), [Adrian Mander](https://www.cardiff.ac.uk/people/view/1499902-mander-adrian), [David Robertson](https://www.mrc-bsu.cam.ac.uk/people/in-alphabetical-order/n-to-s/david-robertson/), and [James Wason](https://www.ncl.ac.uk/medical-sciences/people/profile/jameswason.html).

## Installation

You can install the latest development version of __admtp__ from [Github](https://github.com/) with:

```{r, eval = F}
devtools::install_github("mjg211/admtp")
```

## All

- Questions/Solutions to be added to /inst or vignette?

## Practical 1

- `error_rates()`: Done
- `test_corrections()`: Done
- `power_of_test_corrections()`: Done

## Practical 2

- `mtp_power()`: Needs help details and error checks
- `gMCP()`: Needs help details and error checks
- `calcPower()`: Needs help details and error checks
- `simConfint()`: Needs help details and error checks

## Practical 3

- `des_fixed()`: Done (will add to __OptGS__)
- Uses functions from __mvtnorm__ and __singlearm__ that can be set up to be auto installed
- `practical3.R`: Majority contains no functions

## Practical 4

- `des_fixed()`: Done (will add to __OptGS__)
- Uses functions from __OptGS__ and __MAMS__ that can be set up to be auto installed
- `sim_gs()`: Now available in __OptGS__
- `des_ma()` and `mams_sep()`: Now available in __multiarm__

## Practical 5

- `operatingcharacteristcs_dtl.R`: Now available in __multiarm__
- `allocation()`: Needs help details and error checks
- `differenceinbeta_givenx()`: Needs help details and error checks
- `differenceinbeta()`: Needs help details and error checks
- `findposterior()`: Needs help details and error checks
- `simulateadaptiveenrichment()`: Needs help details and error checks
- `operatingcharacteristics()`: Needs help details and error checks

## Practical 6

- `addarm()`: Needs help details and error checks
- `practical6.R`: No functions

## Practical 7

- `des_triangular()`: Now available in __OptGS__
- `sim_gs()`: Now available in __OptGS__
- `ssre_delta_density()`: Needs help details and error checks
- `ssre_delta_find_e2()`: Needs help details and error checks
- `ssre_delta()`: Needs help details and error checks
- `ssre_sigma()`: Needs help details and error checks

## Practical 8

- All `gMCP_basic.R` files covered above for Practical 2
- `sim_gs()`: Now available in __OptGS__
- `pvaladjp()`: Needs help details and error checks
- `pvaltrunc()`: Needs help details and error checks
- `bonf()`: Needs help details and error checks
- `simes()`: Needs help details and error checks
- `incsimes()`: Needs help details and error checks